Single Bivalent Level Analysis

### 2020-01-27 doc/Bivalent_Analysis.Rmd
last bit o work

# cell is 22nov16_13nov16_MSM_f2_sp1_19 is missing a biv
#cell 5aug17_14jul17_LEW_f1_sp1_11_rev is missing measures for 2 bivs

@@

#remove the incomplete MSM cell
female.whole.cell <- female.whole.cell[female.whole.cell$fileName != "22nov16_13nov16_MSM_f2_sp1_19",]

@@

- is the difference between cell averages for males and females less that 10%?

@@

>>>>

# cell is 22nov16_13nov16_MSM_f2_sp1_19 is missing a biv

#cell 5aug17_14jul17_LEW_f1_sp1_11_rev has broken SC - could be used to compare broken SC

@@

#remove the incomplete LEW female cell
female.whole.cell <- female.whole.cell[female.whole.cell$fileName != "5aug17_14jul17_LEW_f1_sp1_11_rev",]

@@

- Is the difference between cell averages for males and females less that 10%?

@@

** It might be simplier to compare the male and female means, and test it they are greater than the whole cell proprotion of the XX in females cells.**  The XX in a whole female cell contributes ~ 7% of total SC, if the female means for a type of total SC measure are from XX. But I am not using 'whole cell' summaries to compare female and males.

**What is the effect of an extra XX-autosome on single bivalent means?**

use a permutation approach: Make a True data set to start with, same(similar) number of cells, mice and bivalents. Make fake datasets which sample 19 bivalents, for 'in silico' cells for males and females. Also Run cntrl-female data set, where 20 bivalents are sampled, but randomly. Run the same bivalent level summaries for each 'permuted data set'; male avSC, 19Female_avSC, and rand.20_Female_avSC.  The difference between the rand.20 and rand.19 female -permuted data sets should indicate the influence of having an extra 'XX-autosome' in the total dataset.
